Combinatorial Proofs and Decomposition Theorems for First-order Logic

### 2021-01-14 main.tex

\begin{thm}
  Let $\gC$ be a fonet with linking $\linkingof\gC$ and dualizer
  $\dualizer$, and let $A$ be a formula with $\graphof A=\gC$.  Then
  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
\end{thm}

>>>>

\begin{thm}
  Let $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ be given. Then
  the graph $\graphof{\rectif A}$ forms a fonet whose linking is
  $\linkingof{\rectif\Deri}$ and whose dualizer is
  $\substof{\rectif\Deri}$.
\end{thm}

\begin{proof}
  Apply Lemma~\ref{lem:MLS1->fonet} to the rectification $\rectif\Deri$ of $\Deri$.
\end{proof}

\begin{thm}
  Let $\gC$ be a fonet with linking $\linkingof\gC$, let $\dualizer$ be a dualizer
  for $\gC$, and let $A$ be a formula with $\graphof A=\gC$.  Then
  there is a derivation $\vlder{\FOMLS}{\Deri}{A}{\ttt}$ such that
  $\linkingof\gC=\linkingof{\Deri}$ and $\dualizer=\substof{\Deri}$.
\end{thm}
